Diversity, Segregation, and Information in Cities

### 2016-11-04 submission.tex
latest draft

			\caption{
				Spatial analysis of residential segregation in Atlanta and Philadelphia. 
				(\emph{Top}): Percentage of black residents. 
				(\emph{Middle}): Hexgrid of spatial resolution 1km imposed over each city. Within each hex $B$ we compute the local information local information $J_Y(B) = I(X,Y | X \in B)$. 
				(\emph{Bottom}): Numerical summary, including the three information measures.
			} \label{fig:Atlanta_philly}
	\end{figure}

@@

>>>>

			\caption{
				\todo[inline=true]{comment in here that it is possible to walk a km in Atlanta and basically see no change, not so in Philly}
				Spatial analysis of residential segregation in Atlanta and Philadelphia. 
				(\emph{Top}): Percentage of black residents. 
				(\emph{Middle}): Hexgrid of spatial resolution 1km imposed over each city. Within each hex $B$ we compute the local information local information $J_Y(B) = I(X,Y | X \in B)$. 
				(\emph{Bottom}): Numerical summary, including the three information measures.
			} \label{fig:Atlanta_philly}
	\end{figure}

@@

	\todo[inline=true]{Consider plotting the loss-curves in a readable way.}
